Constraining the Interiors of Asteroids Through Close Encounters

### 2022-08-22 paper/main.tex
Ready to run trifecta

Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased density near the center. On the other hand, the lumpy model detects that the two lumps are opposite each other and of roughly the same radius and mass. These radius and mass values are also close to the true values. The model places the lumps correctly near the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect. Uncertainty is also high, due to the extra DOF, however the distribution is in agreement with the extracted density moments because the misplacement of the lumps affects only the $K_{3m}$ density moments, which are not as well constrained as the $K_{2m}$ density moments. The result is a deviation of a few hundred meters in lump location for the reference encounter properties.

>>>>

Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased density near the center. On the other hand, the lumpy model detects that the two lumps are opposite each other and of roughly the same radius and mass. These radius and mass values are also close to the true values. The model places the lumps correctly near the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect. Uncertainty is also high, due to the extra DOF. The difference between the predicted distribution and the true distribution is due entirely to the uncertainty in the moments computed by the fit to flyby data. The density distribution model reproduces those moments perfectly, misplacing the lumps by a few hundred meters because that offset is determined only by the $K_{3m}$ density moments, which are not as well constrained as $K_{2m}$.
